Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-09-19 Paper.tex
Footnote to explain why a 24576 byte limit exists for contract code o

\begin{align}
\quad g' &\equiv \begin{cases}
0 & \text{if} \quad F \\
g^{**} - c & \text{otherwise} \\
\end{cases} \\
\quad \boldsymbol{\sigma}' &\equiv  \begin{cases}
\boldsymbol{\sigma} & \text{if} \quad F \\
\boldsymbol{\sigma}^{**} \quad \text{except:} & \\
\quad\boldsymbol{\sigma}'[a]_c = \texttt{\small KEC}(\mathbf{o}) & \text{otherwise}
\end{cases} \\
\nonumber \text{where} \\
F &\equiv \big(\boldsymbol{\sigma}^{**} = \varnothing \ \vee\  g^{**} < c \ \vee\  |\mathbf{o}| > 24576\big)
\end{align}

>>>>

\begin{align}
\quad g' &\equiv \begin{cases}
0 & \text{if} \quad F \\
g^{**} - c & \text{otherwise} \\
\end{cases} \\
\quad \boldsymbol{\sigma}' &\equiv  \begin{cases}
\boldsymbol{\sigma} & \text{if} \quad F \\
\boldsymbol{\sigma}^{**} \quad \text{except:} & \\
\quad\boldsymbol{\sigma}'[a]_c = \texttt{\small KEC}(\mathbf{o}) & \text{otherwise}
\end{cases} \\
\nonumber \text{where} \\
F &\equiv \big(\boldsymbol{\sigma}^{**} = \varnothing \ \vee\  g^{**} < c \ \vee\  |\mathbf{o}| > 24576\big\text{\footnotemark})
\end{align}
\footnotetext{The 24576 byte limit for output contract code data $\mathbf{o}$ exists because a contract creation call can trigger O(n) cost in terms of reading the code from disk, preprocessing the code for VM execution, and also adding O(n) data to the Merkle proof for the block's proof-of-validity. With higher gas limits that can be caused by dynamic gas limit rules, this is a greater concern, and is especially inconvenient with light clients verifying proofs of validity or invalidity.}
